Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete

### 2015-02-02 main/LMCS.tex
Use \capsabbrev where appropriate

\title{Proof equivalence in MLL is PSPACE-complete}

@@

There have been several proposals for (non-canonical) multiplicative proof nets with units \cite{Blute-Cockett-Seely-Trimble-1996, Koh-Ong-1999, Lamarche-Strassburger-2006, Hughes-2012-nets}, each providing a different take on the proof equivalence problem for \capsabbrev{mll}. We will use the formulation by Hughes \cite{Hughes-2012-nets}, which reduces proof equivalence to a simple rewiring relation, as the basis for our PSPACE-hardness reduction. In this section we will discuss how this notion of proof net arises from the sequent calculus, and introduce a compact notation for it.

@@

The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs. This problem is PSPACE-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.

@@

\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps. This is the problem shown to be PSPACE-complete by Hearne and Demaine \cite{GamesPuzzlesAndComputation}:

@@

The PSPACE-completeness of NCG-reconfiguration may seem surprising at first. To give a feel for the dynamics that make this problem \capsabbrev{pspace}-hard, we shall exhibit an example where an exponentially-long reconfiguration sequence is needed. The existence of such rewiring sequences is an essential property for the hardness result: if reconfiguration sequences could be given a polynomial bound, they would be polynomial-time witnesses, placing the problem within NP.

>>>>

\title{Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete}

@@

There have been several proposals for (non-canonical) multiplicative proof nets with units \cite{Blute-Cockett-Seely-Trimble-1996, Koh-Ong-1999, Lamarche-Strassburger-2006, Hughes-2012-nets}, each providing a different take on the proof equivalence problem for \capsabbrev{mll}. We will use the formulation by Hughes \cite{Hughes-2012-nets}, which reduces proof equivalence to a simple rewiring relation, as the basis for our \capsabbrev{pspace}-hardness reduction. In this section we will discuss how this notion of proof net arises from the sequent calculus, and introduce a compact notation for it.

@@

The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs. This problem is \capsabbrev{pspace}-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.

@@

\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps. This is the problem shown to be \capsabbrev{pspace}-complete by Hearne and Demaine \cite{GamesPuzzlesAndComputation}:

@@

The \capsabbrev{pspace}-completeness of \capsabbrev{ncg}-reconfiguration may seem surprising at first. To give a feel for the dynamics that make this problem \capsabbrev{pspace}-hard, we shall exhibit an example where an exponentially-long reconfiguration sequence is needed. The existence of such rewiring sequences is an essential property for the hardness result: if reconfiguration sequences could be given a polynomial bound, they would be polynomial-time witnesses, placing the problem within NP.
